Online resolving assembly graph by ONT long reads data

### 2019-10-25 paper.tex
sbs

It is worth noting that due to dead-ends, there not always exist a path in the assembly graph connecting two anchors as suggested by the alignments. In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is used for a \emph{pseudo} edge being created.
\subsection{Resolve by reducing the graph complexity}

>>>>

It is worth noting that due to dead-ends, there not always exist a path in the assembly graph connecting two anchors as suggested by the alignments. In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is contained in a \emph{pseudo} edge.
\subsection{Resolve the graph by reducing its complexity}
